DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-28 paper/intro.tex
still revising

% broad context:
% - advance in ai sparked interests in the robotics application, such as
%   self-driving cars.
% - in particular, deep neural network models are increasingly used
%   for perception and control of a vehicle. say. AI workloads.
%
% 
Self-driving cars have been a topic of increasing interest in recent
years as multiple companies are actively developing related
technologies. One of the key technologies is the use of deep neural
network (DNNs) models for preception and control of the vehicle.

% requirements:
%   (1) real-time processing.
%   (2) cost
%   (3) safety
%   (4) SWaP
%
% our goals:
%   (1) build a safe and low cost testbed but utilizing the
%       state-of-the-art AI technologies: DNN based end-to-end control
%   (2) analyze real-time issues in DNN based end-to-end control.
%   (3) evalute popular embedded platforms for the AI workloads
%       (end-to-end control, perception).
%       - Can apsberry pi handle AI workloads?
%       - Can embedded GPU do better? How much?
\fixme{TBD: requirements and goals reivison}
it is necessary that all real-time operations are successfully
performed prior to their deadlines. This requires that the AV platform
be capable of completing all necessary computations in a timely
manner, while maintaining a high level of accuracy. Consequently, the
cost of creating a platform capable of self-driving can be relatively
high, especially in the current cost-sensitive climate of the
automotive industry \cite{}. The overall price for an autonomous
vehicle platform currently acts as a bottleneck, especially from an
academic standpoint, where cost is an important factor. For many
researchers and students, the charge associated with autonomous
vehicle research is a significant barrier. These same parties may also
be deterred from participating in autonomous vehicle research due to
the potential for their developed platforms to break in the
experimental process. The idea of building one relatively expensive
platform may not be too daunting for some, but the notion of
potentially making multiple identical platforms in case of accidents
may be overwhelming. Toward this end, we explore the possibility of
developing a low-cost system that still employs state-of-the-art AI
technologies and is capable of executing real-time autonomous vehicle
operations.

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$200 in total).
The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN).
The network receives an image frame from a single forward
looking camera, as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}. 
The network is deep as it has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is in fact identifical to the one
used in Nvidia's DAVE-2 self-driving car~\cite{Bojarski2016}. Other
than the obvious difference in scale (RC car vs. real car), from the
computing perspective, the only differences between
the two systems are that our system is implemented in
TensorFlow~\cite{abadi2016tensorflow} and runs on a 
Raspberry Pi 3 whereas Nvidia's DAVE-2 systems is implemented in Torch
7~\cite{collobert2011torch7} and runs on a Drive PX computer (NVIDIA's
automotive specialized computing system~\cite{drivepx}), which is more
powerful but also more expensive.

% how we trained and tested (in terms of network performance)
We follow the standard supervised learning methodology to train the
system with a goal of following lanes on the ground, mimicking real
roads. We first collected data for taining and validation by manually 
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
equips a Nvidia GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform interference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each \emph{inference} operation must
be completed within the desired control period. (e.g., 50ms period for
20Hz control frequency.)

>>>>

% broad context:
% - advance in ai sparked interests in the robotics application, such as
%   self-driving cars.
% - in particular, deep neural network models are increasingly used
%   for perception and control of a vehicle. say. AI workloads.
%
%
Autonomous cars have been a topic of increasing interest in recent
years as many companies are actively developing related hardware
and software technologies for ever more autonomous decision making
capabilities---ultimately fully autonomous driving capability without
any human intervention. One of the key technologies for increased
autonomy of a vehicle is deep neural network (DNN) models, which have
been sucessfully applied in various perception and control tasks in
recent years. Already, DNN models are used in commercial
semi-autonomous vehicles such as Tesla Model S, which includes a poweful
computer and accelerators (e.g., MobileEye EyeQ) to execute various
DNN models, espeically for (vision-based) real-time perception
tasks. DNN based end-to-end control of a vehicle is also actively
explored in recent years~\cite{Bojarski2016}.

% requirements:
%   (1) real-time processing.
%   (2) cost
%   (3) safety
%   (4) SWaP
%
% our goals:
%   (1) build a safe and low cost testbed but utilizing the
%       state-of-the-art AI technologies: DNN based end-to-end control
%   (2) analyze real-time issues in DNN based end-to-end control.
%   (3) evalute popular embedded platforms for the AI workloads
%       (end-to-end control, perception).
%       - Can apsberry pi handle AI workloads?
%       - Can embedded GPU do better? How much?
There are several challenges in studying autonomous vehicles.

it is necessary that all real-time operations are successfully
performed prior to their deadlines. This requires that the AV platform
be capable of completing all necessary computations in a timely
manner, while maintaining a high level of accuracy. Consequently, the
cost of creating a platform capable of self-driving can be relatively
high, especially in the current cost-sensitive climate of the
automotive industry \cite{}. The overall price for an autonomous
vehicle platform currently acts as a bottleneck, especially from an
academic standpoint, where cost is an important factor. For many
researchers and students, the charge associated with autonomous
vehicle research is a significant barrier. These same parties may also
be deterred from participating in autonomous vehicle research due to
the potential for their developed platforms to break in the
experimental process. The idea of building one relatively expensive
platform may not be too daunting for some, but the notion of
potentially making multiple identical platforms in case of accidents
may be overwhelming. Toward this end, we explore the possibility of
developing a low-cost system that still employs state-of-the-art AI
technologies and is capable of executing real-time autonomous vehicle
operations.

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$200 in total).
The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}. 
The network is \emph{deep} as it has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is in fact identifical to the one
used in NVIDIA's DAVE-2 self-driving car~\cite{Bojarski2016}. Other
than the obvious difference in scale (RC car vs. real car) the only
differences between the two systems---from the computing
perspective---are that our system is implemented in 
TensorFlow~\cite{abadi2016tensorflow} and runs on a 
Raspberry Pi 3 whereas NVIDIA's DAVE-2 systems is implemented in Torch
7~\cite{collobert2011torch7} and runs on a Drive PX computer (NVIDIA's
automotive specialized computing system~\cite{drivepx}), which is more
powerful but also more expensive.

% how we trained and tested (in terms of network performance)
We follow the standard supervised learning methodology to train the
system with a goal of following lanes on the ground, mimicking real
roads. We first collected data for taining and validation by manually 
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
equips a NVIDIA GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform interference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each \emph{inference} operation must
be completed within the desired control period. (e.g., 50ms period for
20Hz control frequency.)
